---
output:
  word_document: default
  html_document: default
---

```{r}
library(tidyverse)
library(tidymodels)
```

```{r}
library(readr)
trucks <- read_csv("trucks.csv")
View(trucks)
head(trucks)
```

```{r}
ggplot(trucks, aes(Distance, Speeding)) +
  geom_point(alpha = 0.4) + theme_bw()
```

Task 1-
Huge relationship. Since "speeding is really a measure of time, this would mean that the drivers were mostly driving for a short period of time but they were either going slowly for 10 minutes and didn't go far, or they were driving very fast for 10 minutes and covered a much greater distance. Either way, no one drove a medium distance. ALso, very few people drove for a long time, and no one drove for a long time over a short distance. I would guess ther should be 4 clusters.


```{r}
str(trucks)
summary(trucks)
```

```{r}
kmeans_recipe = recipe(~ Distance + Speeding, trucks) 

trucks_dummy = kmeans_recipe %>% 
  step_dummy(all_nominal(), one_hot = TRUE) %>%
  step_scale(all_numeric()) %>%
  step_center(all_numeric()) 

trucks_dummy = prep(trucks_dummy, trucks) #prepares the recipe

trucks_cleaned = bake(trucks_dummy, trucks) #applies the recipe and yields a data frame
```


```{r}
set.seed(64)
clusts = 
  tibble(k = 2) %>%
  mutate(
    kclust = map(k, ~kmeans(trucks_cleaned, .x)),
    tidied = map(kclust, tidy),
    glanced = map(kclust, glance),
    augmented = map(kclust, augment, trucks_cleaned)
  )

clusts
```


```{r}
clusters = 
  clusts %>%
  unnest(cols = c(tidied))

assignments = 
  clusts %>% 
  unnest(cols = c(augmented))

clusterings = 
  clusts %>%
  unnest(cols = c(glanced))
```

```{r}
p1 = 
  ggplot(assignments, aes(x = Distance, y = Speeding)) +
  geom_point(aes(color = .cluster), alpha = 0.8) + 
  facet_wrap(~ k)
p1
```
```{r}
set.seed(412)
clusts2 = 
  tibble(k = 1:8) %>%
  mutate(
    kclust = map(k, ~kmeans(trucks_cleaned, .x)),
    tidied = map(kclust, tidy),
    glanced = map(kclust, glance),
    augmented = map(kclust, augment, trucks_cleaned)
  )

clusts2
```

```{r}
clusters2 = 
  clusts2 %>%
  unnest(cols = c(tidied))

assignments2 = 
  clusts2 %>% 
  unnest(cols = c(augmented))

clusterings2 = 
  clusts2 %>%
  unnest(cols = c(glanced))
```



```{r}
p1 = 
  ggplot(assignments2, aes(x = Distance, y = Speeding)) +
  geom_point(aes(color = .cluster), alpha = 0.8) + 
  facet_wrap(~ k)
p1
```
Task 5-
I am still convinced that 4 is the best as it evenly divides the people who drive far and short as well as the people for a long time and those that drive for a shorter amount of time.


```{r}
set.seed(64)
clusts = 
  tibble(k = 4) %>%
  mutate(
    kclust = map(k, ~kmeans(trucks_cleaned, .x)),
    tidied = map(kclust, tidy),
    glanced = map(kclust, glance),
    augmented = map(kclust, augment, trucks_cleaned)
  )

clusts
```

```{r}
clusters = 
  clusts %>%
  unnest(cols = c(tidied))

assignments = 
  clusts %>% 
  unnest(cols = c(augmented))

clusterings = 
  clusts %>%
  unnest(cols = c(glanced))
```

```{r}
p1 = 
  ggplot(assignments, aes(x = Distance, y = Speeding)) +
  geom_point(aes(color = .cluster), alpha = 0.8) + 
  facet_wrap(~ k)
p1
```

Task 6-
This looks great. This clearly has 4 defined parts and each of them has roughly the same amount of drivers. 4 is my choice for the most optimal amount of clusters.









